Future challenges for Research Software Engineering

### 2025-05-17 future_challenges_for_RSEng.tex
change tense
we want to full programme of lovely sun not only at the end of the day

\begin{story}{Introduction}{intro}
In order to give a more concrete setting, imagine a world ten years from now.
Not too much to be overwhelmingly far in the future, but distant enough for some changes to occur.
Over this time frame Kim\cite{Anzt2021} and Kay\cite{Goth2024},
our fictional RSEs who we have used to illustrate specific scenarios in our earlier work,
were able to ride the waves of their career in Research Software Engineering and are now pondering early retirement on a sunset blessed beach.
%MM-NOTE: the above scenario (early retirement) is contrary to all trends in retirement age development of public employees across the "global north".
But the world has moved on.
When they look back, what will they see as problems which are now solved?
Which tasks are still relevant, where they can be happy that a younger generation is now taking up the baton and carrying forward their work?
What issues have newly emerged, where they are now just happy to say: “Oh well… my successors will take care of that”.
In order to bring this future to life, these two personas will accompany us through the rest of this paper and we will shed light on aspects
of their future in respective small story boxes.
 \end{story}

>>>>

\begin{story}{Introduction}{intro}
In order to give a more concrete setting, imagine a world ten years from now.
Not too overwhelmingly far ahead in the future, but distant enough for some changes to have occurred.
Over this time frame Kim\cite{Anzt2021} and Kay\cite{Goth2024},
our fictional RSEs who we have used to illustrate specific scenarios in our earlier work,
were able to ride the waves of their career in Research Software Engineering and are now pondering early retirement on a sun blessed beach.
%MM-NOTE: the above scenario (early retirement) is contrary to all trends in retirement age development of public employees across the "global north".
But the world has moved on.
When they look back, what will they see as problems which are now solved?
Which tasks are still relevant, where they can be happy that a younger generation is now taking up the baton and carrying forward their work?
What issues have newly emerged, where they are now just happy to say: “Oh well… my successors will take care of that”.
In order to bring this future to life, these two personas will accompany us through the rest of this paper and we will shed light on aspects
of their future in respective small story boxes.
 \end{story}
